### 2016-10-19 Multi-scale_Mobility_Pattern_CEUS/template-num.tex
init

%  LaTeX support: latex@mdpi.com
%  In case you need support, please attach all files that are necessary for compiling as well as the log file, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).

% You need to save the "mdpi.cls" and "mdpi.bst" files into the same folder as this template file.

%=================================================================
\documentclass[ijgi,article,accept,moreauthors,pdftex,10pt,a4paper]{mdpi}

%=================================================================
\firstpage{1}
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother 
\articlenumber{x}
\doinum{10.3390/------}
\pubvolume{xx}
\pubyear{2016}
\copyrightyear{2016}
\externaleditor{Academic Editors: Marguerite Madden and Wolfgang Kainz}
\history{Received: 15 August 2016; Accepted: 28 September 2016; Published: date}
%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed

%=================================================================

\usepackage{placeins}

%% Please use the following mathematics environments:
 \theoremstyle{mdpi}
 \newcounter{thm}
 \setcounter{thm}{0}
 \newcounter{ex}
 \setcounter{ex}{0}
 \newcounter{re}
 \setcounter{re}{0}

 \newtheorem{Theorem}[thm]{Theorem}
 \newtheorem{Lemma}[thm]{Lemma}
 \newtheorem{Corollary}[thm]{Corollary}
 \newtheorem{Proposition}[thm]{Proposition}

 \theoremstyle{mdpidefinition}
 \newtheorem{Characterization}[thm]{Characterization}
 \newtheorem{Property}[thm]{Property}
 \newtheorem{Problem}[thm]{Problem}
 \newtheorem{Example}[ex]{Example}
 \newtheorem{ExamplesandDefinitions}[ex]{Examples and Definitions}
 \newtheorem{Remark}[re]{Remark}
 \newtheorem{Definition}[thm]{Definition}
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
%\Title{Exploring multi-scale spatiotemporal Twitter user mobility patterns with a scalable visual-analytics framework}
\Title{Exploring Multi-Scale Spatiotemporal Twitter User Mobility Patterns with a Visual-Analytics Approach}

% Authors, for the paper (add full first names)
\Author{Junjun Yin $^{1,3}$ and Zhenhong Du $^{2,3,*}$}
% Authors, for metadata in PDF
\AuthorNames{Junjun Yin and Zhenhong Du}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Department of Geography and Geographic Information Science, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA; jyn@illinois.edu\\
$^{2}$ \quad Institute of Geographic Information Science, School of Earth Sciences, Zhejiang University, Hangzhou 310028, China; duzhenhong@zju.edu.cn\\
$^{3}$ \quad CyberGIS Center for Advanced Digital and Spatial Studies, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA}

% Contact information of the corresponding author
\corres{Correspondence: duzhenhong@zju.edu.cn; Tel.: +86-138-1919-2989}

% Current address and/or shared authorship

% Simple summary
%\simplesumm{}

% Abstract (Do not use inserted blank lines, i.e. \\) 
\abstract{Understanding human mobility patterns is of great importance for urban planning, traffic management, and even marketing campaign.
However, the capability of capturing detailed human movements with fine-grained spatial and temporal granularity is still limited.
In this study, we extracted high-resolution mobility data from a collection of over 1.3 billion geo-located Twitter messages.
Regarding the concerns of infringement on individual privacy, such as the mobile phone call records with restricted access, the dataset is collected from publicly accessible Twitter data streams.
In this paper, we employed a visual-analytics approach to studying multi-scale spatiotemporal Twitter user mobility patterns in the contiguous United States during the year 2014.
Our approach included a scalable visual-analytics framework to deliver efficiency and scalability in filtering large volume of geo-located tweets, modeling and extracting Twitter user movements, generating space-time user trajectories, and summarizing multi-scale spatiotemporal user mobility patterns.
We performed a set of statistical analysis to understand Twitter user mobility patterns across multi-level spatial scales and temporal ranges.
In particular, Twitter user mobility patterns measured by the displacements and radius of gyrations of individuals revealed multi-scale or multi-modal Twitter user mobility patterns.
By further studying such mobility patterns in different temporal ranges, we identified both consistency and seasonal fluctuations regarding the distance decay effects in the corresponding mobility patterns.
At the same time, our approach provides a geo-visualization unit with an interactive 3D virtual globe web mapping interface for exploratory geo-visual analytics of the multi-level spatiotemporal Twitter user movements.}

% Keywords
\keyword{Geo-located tweets, mobility patterns, multi-scale spatiotemporal analysis, scalable visual-analytics framework}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Sections that are not mandatory are listed as such. The section titles given are for Articles. Review papers and other article types have a more flexible structure.

%% Only for the journal Gels: Please place the Experimental Section after the Conclusions

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Understanding human mobility patterns is of great importance for a broad range of applications from urban planning~\cite{zheng2008understanding}, traffic management~\cite{jiang2009characterizing}, and even the spatial spread of epidemic diseases~\cite{belik2011natural}.
Earlier research efforts relied on low-resolution mobility data to understand human mobility patterns, such as using census records to study human migration patterns~\cite{greenwood1985human}, or delivering questionnaires and asking volunteers to report the track of bank notes to infer human travel patterns~\cite{brockmann2006scaling}.
However, such mobility data do not provide detailed human movements with fine-grained spatial and temporal granularity, which are usually aggregated and therefore are limited to capture mobility patterns of individuals~\cite{gonzalez2008understanding,Jurdak2015}.
In addition to the mobility data collected by GPS trackers~\cite{zheng2008understanding, rhee2011levy} and mobile phone call records~\cite{gonzalez2008understanding,sevtsuk2010does,kung2014exploring}, emerging as a new mobility data source, today's pervasive Location Based Social Media (LBSM) platforms (e.g., Twitter and Foursquare) offer continuous spatial Big Data streams with massive amount of detailed and frequently updated user digital footprints in the form of real-world user trails and footprints~\cite{thatcher2014living}.
A significant advantage of utilizing LBSM data streams as proxies for studying human mobility patterns is the large spatial coverage.
For instance, researchers have used geo-located tweets for studying global mobility patterns~\cite{hawelka2014geo}, which is otherwise impossible for other mobility datasets (e.g., GPS traces and mobile phone call records).
Regarding the concerns of infringement on individual privacy, such as the mobile phone call records with restricted access~\cite{giannotti2008mobility,crampton2014collect,Jurdak2015}, the publicly available LBSM data streams offer unique opportunities for conducting reproducible and comparative scientific findings across different geographic regions.

Many recent studies have adopted LBSM data streams to study human mobility patterns.
For example, they modeled and extracted trajectories of individuals and performed statistical analysis focusing on the distance decay effects in the collective user movements~\cite{gonzalez2008understanding}, which were used to reveal different travel modes~\cite{Jurdak2015}, travel demands~\cite{wu2014intra,hasan2013understanding}, and the impact of social connections~\cite{cho2011friendship}.
These studies have provided strong supports for using LBSM data as proxies for studying mobility patterns of individuals and valuable insights into human mobility dynamics.
However, the variations of movements in different spatial scales and temporal ranges are neglected in these studies, where the measurements of distances are either fixed in a certain time range or to a specific geographic region.
For instances, the examinations on whether there are temporal (e.g., monthly or seasonal) changes within the movements or how the observed mobility patterns vary across different spatial scales (e.g., intra- or inter city or national levels) are lacking.
Such insights are critical to advance our understandings of the collective mobility patterns for various applications, such as examining the mobility patterns across different cities~\cite{noulas2012tale}, the spread patterns of disease~\cite{balcan2009multiscale, tamerius2011global} and touristic activities~\cite{hawelka2014geo}.
On the other hand, while the high-resolution spatiotemporal records from LBSM present unique research opportunities in this direction, the inherited large data volume poses significant data-intensive challenges for developing multi-scale spatiotemporal analysis approaches to dealing with the complexities in filtering movements of individuals, modeling and aggregating user trajectories at multiple spatial and temporal scales~\cite{tsou2015}.

In this paper, we have employed a visual-analytics approach to exploring the Twitter user mobility patterns across multi-level spatial scales and temporal ranges in the continuous United States (i.e., excluding Alaska and Hawaii) during the year 2014.
The mobility data is extracted from over 1.3 billion geo-located Twitter messages (i.e., tweets) from 1st January to 31st December 2014 over North America with over 6 million Twitter users and over 1 TB in file size.
To address the data-intensive challenge embedded in this dataset, we have developed a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets.
This framework is implemented based on high-performance distributed computing environment using Apache Hadoop (http://hadoop.apache.org/), which is an open source software framework to enable distributed processing of large datasets across computing clusters.
Enabled by this framework, we have performed a set of statistical analysis to understand multi-scale spatiotemporal Twitter user mobility patterns. 
We have modeled the frequency of Twitter users visiting different locations to study the collective user visiting behaviors, where we have identified temporal similarities in the distributions.
In particular, Twitter user mobility patterns measured by user displacements and radius of gyrations of individuals~\cite{gonzalez2008understanding} have revealed different groups of Twitter users with multi-scale or multi-modal mobility patterns and multiple travel modes~\cite{Jurdak2015}.
By further studying such mobility patterns in different temporal ranges, we have identified both consistency and seasonal fluctuations regarding the distance decay effects in the corresponding mobility patterns.
In addition, our approach provides an interactive 3D virtual globe web mapping interface to enable exploratory geo-visual analytics for understanding the detailed Twitter user movement flows within a given spatial scale and time window.

The remainder of this paper is organized as follows.
Section 2 describes the related work in the context of studying mobility patterns using LBSM data, in particular, the geo-located Twitter data.
We focus on research challenges in using visual-analytics methods to enable multi-scale spatiotemporal analysis with massive movement datasets, including data management, multi-level spatiotemporal user trajectory modeling and visualization.
Section 3 details the processes for extracting, aggregating and summarizing multi-level spatiotemporal Twitter user mobility patterns.
Section 4 presents the case study of performing visual-analytics for seeking multi-scale spatiotemporal Twitter mobility patterns in the continuous United States of the year 2014.
Section 5 concludes the paper.

\section{Mobility Patterns in Location Based Social Media data}
\subsection{Geo-located Twitter Data for Studying Large-scale User Movements}
To understand detailed mobility patterns of individuals, the capability to capture human movements with fine-grained spatial and temporal granularity is critical.
In this connection, using GPS trackers tends to produce, to date, the most accurate records of individuals' movements regarding the accuracy of recorded user locations and update frequency~\cite{zheng2008understanding}.
However, such data are often limited in spatial scale (e.g., within a specific city or region) from a small group of people, for example, 226 and 182 volunteers participated in collecting such mobility data in~\cite{rhee2011levy} and~\cite{zheng2010geolife} respectively.
Other than tracking people directly, the vehicle-based GPS traces are often tied to specific vehicles (e.g. taxi), which are only accessible for a certain group of people~\cite{kung2014exploring}.

Another approach from the literatures for studying human mobility is using mobile phone call data, such as Call Detail Records (CDR), where the locations of mobile users are estimated by cell tower triangulation with an accuracy in the order of kilometers~\cite{gonzalez2008understanding,sevtsuk2010does,kung2014exploring}.
Such a dataset can cover relatively large spatial scale~\cite{becker2013human,sobolevsky2013delineating} (e.g., national level) and a large portion of the population in the study region~\cite{kung2014exploring}.
However, due to the concerns of infringement on individual privacy, mobile phone call data are not publicly accessible at all.
Even such data were obtained in the mentioned studies, they came from various service providers covering different groups of users.
These issues limit the capability for conducting reproducible scientific findings for mobility research, such as validating or extending the existing discoveries.

In this connection, it becomes increasingly popular for researchers to exploit the publicly accessible mobility data captured from today's pervasive Location Based Social Media (LBSM) platforms (e.g., Foursquare and Twitter).
LBSM enables users to attach their current location as a geo-tag to the message they post, which is derived from either the GPS or Wi-Fi positioning with a high position resolution down to 10 meters~\cite{Jurdak2015}.
A Big Data scenario emerges when millions social media users constantly post messages.
In this study, geo-located Twitter data are chosen as a source for studying detailed mobility patterns.
Compared to other LBSM platforms, Twitter is one of the most popular platforms and is been actively used in many countries.
It provides a publicly accessible streaming API for easy data access~\cite{twitterAPI}.
Indeed, many other LBSM data can be collected from the data streams, such as Foursquare check-in data~\cite{cranshaw2012livehoods,hasan2013understanding}.

However, it is worth noting that there are some limitations and complexities in directly using LBSM data for studying human mobility patterns.
For example, comparing to GPS traces, the update frequency of an individual's location varies depending on when a user is posting a new geo-located message or check-in at a new place.
Although geo-located tweets tend to provide geo-locations with high position resolution as aforementioned~\cite{Jurdak2015}, the information regarding the quality of the geo-locations is absent in each tweet.
This will contribute to the uncertainties in calculating the distance of Twitter user movements, especially in densely built environments.   
There is also a potential mismatch regarding the representativeness of the overall population since not all people use social media or send geo-located messages~\cite{kung2014exploring}, the demographic information of the Twitter users cannot be easily identified.
The derived mobility patterns may lead to an over or under-representation of the real-world human mobility patterns.
Many studies started to look into the demographic information of LBSM data, in particular Twitter data~\cite{mitchell2013geography,longley2015geotemporal}.
Although the used methods are still arguable, these issues certainly require us to pose stricter criteria in understanding human mobility patterns using geo-located Twitter data.
On the other hand, geo-located Twitter dataset presents some unique advantages that make it a valuable proxy for studying human mobility patterns.
For example, the high-resolution location information enables to identify multiple travel modes in user mobility patterns~\cite{Jurdak2015}; the large spatial coverage enables to study global mobility patterns~\cite{hawelka2014geo}, which is almost impossible for other mobility datasets.
More importantly, by continuously monitoring the geo-located Twitter data streams with large volume of detailed and frequently updated spatiotemporal records of Twitter users, it offers a great deal of potential for studying mobility patterns of large groups of individuals at different spatial scales (e.g., movements across cities, states or even countries) and temporal gratuity (e.g., weekly, monthly, and seasonal movements), which is one of the motivations for this study.

\subsection{Data-intensive Challenges for Multi-scale Geo-visual Analytics}
Mobility data are essentially a collection of spatiotemporal records of people re-allocating across the geographic space.
To study mobility patterns of individuals, a space-time trajectory of each individual user should be modeled and constructed to quantify the collective movements over space and time.
Based on the extracted space-time trajectories, aforementioned studies are able to perform analysis, such as the measurements of user displacements and radius of gyrations of individuals, to study the mobility dynamics.
Indeed, space-time trajectory is one of the core concepts in H{\"a}gerstrand's time geography to understand the embedded spatiotemporal dynamics~\cite{hagerstrand1985time}, which has provided useful insights to explore movements across different geographical scales and temporal ranges.
For example, a geo-visualization approach was used to study human activity patterns, where user trajectories were mapped in a 3D space ordered by timestamps in the third dimension~\cite{kwan2004geovisualization}.
While such an approach enables visualization of individual trajectories, its capability is limited in dealing with large-volume movement datasets~\cite{andrienko2007designing}.
Instead of directly visualizing an individual user's trajectories, a space-time cube approach was proposed to analyzing and visualizing the collective trajectories.
It provides flexibilities in setting up both spatial scales and temporal ranges, and therefore is used to study mobility patterns across different spatial units (e.g., countries, states, and cities, etc.) and identify the changes over space and time~\cite{maceachren2001research, maceachren2004maps}.
In this regard, visual-analytics methods are proposed to better convey the findings in terms of analyzing and visualizing multi-level spatiotemporal mobility patterns~\cite{andrienko2007designing,andrienko2007visual}.
Visual-analytics methods focus on the synergy of computational and analytical methods to reduce the visual clutter, where aggregation methods are suggested to perform grouping/dividing individual's moving trajectories at different spatial and temporal granularity, e.g., utilizing the space-time cube approach~\cite{andrienko2007designing}.
Employing visual-analytics methods dealing with massive movement datasets is not only beneficial for optimizing visualizations but also provides a great deal of flexibilities for performing statistical analysis in seeking mobility patterns with different level of spatiotemporal details.

However, in the context of studying mobility patterns using large volume of geo-located Twitter data, the inherited large data volume poses significant data intensive challenges for visual-analytics methods to scale with both the data volume and the computational requirements (e.g., movement extraction and trajectory modeling)~\cite{cao2014scalable}.
In particular, in our study, 1.3 billion geo-located tweets were collected with over 1 TB in file size.
To construct a space-time trajectory of an individual, it is necessary to go through the massive dataset to sort and update the trajectory whenever a new location is found.
Such a task is already computationally demanding, let along breaking the trajectories to construct space-time cube with multiple spatial scale and temporal ranges.
Indeed, developing a multi-scale spatiotemporal analysis approach is identified as one of the research challenges for dealing with social media Big Data~\cite{tsou2015}.
To address the data-intensive challenges, there is a need to develop a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets for studying multi-level spatiotemporal Twitter user mobility patterns.

\section{Materials and Methods}
\subsection{Geo-located Twitter Data}
Geo-located tweets are tweets appended with an additional geo-tag in the form of a pair of geographical coordinates, which represents the location a tweet was sent at.
In this study, the geo-located tweets were downloaded using the Twitter Streaming API, where we specified a geographical bounding box as an area-of-interest to retrieve all the geo-located tweets that fall within it.
To ensure complete coverage over the continuous United States, we implemented a crawler that selects North America as the initial area-of-interest, where the geographical boundary is specified with lower left (latitude: 5.4, longitude: -167.3) and upper right (latitude: 83.2, longitude: -52.2).
The crawler is constantly running with over 2 million geo-located raw tweets ($\sim$2 GB in size) collected per day.
We have collected more than 1.3 billion geo-located tweets from 1 January to 31 December 2014 with 6,147,430 Twitter users and 1 TB in file size.

In particular, this data collection of the year 2014 was originally used to map the spatial spread of flu in North America during the time period~\cite{padmanabhan2014flumapper}.
As a social media account is not equal to a real person in the physical world~\cite{tsou2015}, to ensure the data quality, the collected raw tweets were further filtered by the following steps: We first removed duplicated messages in the dataset~\cite{black2012twitter}; and then we removed non-human users based on the heuristic of unusual relocating speed discussed in~\cite{hawelka2014geo,Jurdak2015}.
In this case, we adopted the speed limit value as 240 m/s used in~\cite{Jurdak2015}, where we examined all the consecutive locations of each user and excluded those with relocating speed over the limit.
Note that the original location information embedded in each geo-located tweet is given in units of latitude and longitude, the distance is calculated by the great-circle distance between two points on a sphere with the haversine formula.
Finally, we used the geographic boundaries of the continuous United States (excluding Alaska and Hawaii) to further restrict the remaining tweets, where the technical details is presented in the following section. Based on these reinforcements, the dataset contains 1,052,861,000 tweets and 4,559,205 unique users.

\subsection{A scalable visual-analytics framework}
To address the data-intensive challenges, we have developed a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets for studying multi-level spatiotemporal Twitter user mobility patterns.
The scalable visual-analytics framework consists of two main units: (1) Data processing unit: a distributed computing environment using Apache Hadoop for modeling and extracting Twitter user movements, generating space-time user trajectories, and summarizing the movements at multiple spatiotemporal scales.
(2) Geo-visualization unit: an interactive 3D virtual globe web mapping interface for exploratory geo-visual analytics to understand detailed Twitter user movement flows across different spatial scales and temporal ranges.

Apache Hadoop combines a distributed file system, namely Hadoop Distributed File System(HDFS)~\cite{shvachko2010hadoop} with MapReduce programming paradigm~\cite{dean2008mapreduce}, which can be applied to a wide range of data-intensive problems.
Our framework benefits from using Hadoop in both data management and processing.
First, since the input data is large it is desirable to store it on multiple machines.
This provides scalability in relation to the growth of data size, where Hadoop can scale to more computing nodes in a cluster to maintain the performance.
Second, by using Hadoop we can parallelize the computational tasks, where MapReduce breaks the entire computation into small tasks and schedule them among different computing nodes, to make the data processing faster and more efficient.
An overall system architecture of the framework is shown in Figure~\ref{fig:overall_archi}.
The details regarding the function and implementation of each unit are presented in the next sections.

\begin{figure}[ht]
\centering
\includegraphics[width=0.55\linewidth]{./figures/Overall_Architecture222}
\caption{The overall system architecture of the framework.}
\label{fig:overall_archi}
\end{figure}
\FloatBarrier

\subsection{Space-time Twitter User Trajectories}
To derive meaningful mobility patterns of individuals, a space-time trajectory of each individual user should be constructed~\cite{hagerstrand1985time}.
Each raw geo-located tweet contains multiple fields of information, such as the created time, country, language code, and location, etc.
To construct a space-time trajectory from the data collection, we are interested in the following fields: \textit{user ID, location, timestamp}, which can be represented by a tuple $\left\langle id, loc, t\right\rangle$, where \textit{id} is a unique string representing a Twitter user's id; \textit{loc} is the recorded location of the message represented as a pair of projected coordinates $\left\langle x, y\right\rangle$;
and \textit{t} is the timestamp of when the message was posted; A Twitter user's space-time trajectory is defined as follows.
\newline

\noindent\textbf{Definition 1. Space-time Twitter user trajectory:} \emph{The space-time trajectory of a Twitter user is defined as a collection of recorded geo-locations in the chronological order (i.e., based on the attached timestamp):} 
\newline

$Trajectory_{user_{id}} \equiv \lbrace \langle id, loc_{1}, t_{1}\rangle, \langle id, loc_{2}, t_{2}\rangle, \langle id, loc_{i}, t_{i}\rangle, ... \langle id, loc_{n}, t_{n}\rangle \rbrace, i = 1, 2, 3...n$
\newline

>>>>

% Template article for preprint document class `elsart'
% SP 2006/04/26

\documentclass{elsart}

% Use the option doublespacing or reviewcopy to obtain double line spacing
% \documentclass[doublespacing]{elsart}

% if you use PostScript figures in your article
% use the graphics package for simple commands
% \usepackage{graphics}
% or use the graphicx package for more complicated commands
% \usepackage{graphicx}
% or use the epsfig package if you prefer to use the old commands
% \usepackage{epsfig}

% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}

% The lineno packages adds line numbers. Start line numbering with
% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
% for the whole article with \linenumbers.
% \usepackage{lineno}

% \linenumbers
\begin{document}

\begin{frontmatter}

% Title, authors and addresses

% use the thanksref command within \title, \author or \address for footnotes,
% use the corauthref command within \author for corresponding author footnotes,
% use the ead command for the email address,
% and the form \ead[url] for the home page:
% \title{Title\thanksref{label1}}
% \thanks[label1]{}
% \author{Name\corauthref{cor1}\thanksref{label2}}
% \ead{email address}
% \ead[url]{home page}
% \thanks[label2]{}
% \corauth[cor1]{}
% \address{Address\thanksref{label3}}
% \thanks[label3]{}

\title{}

% use optional labels to link authors explicitly to addresses:
% \author[label1,label2]{}
% \address[label1]{}
% \address[label2]{}

\author{}

\address{}

\begin{abstract}
% Text of abstract
\end{abstract}

\begin{keyword}
% keywords here, in the form: keyword \sep keyword

% PACS codes here, in the form: \PACS code \sep code
\PACS 
\end{keyword}
\end{frontmatter}

% main text
\section{}
\label{}

% The Appendices part is started with the command \appendix,
% appendix sections are then done as normal sections
% \appendix

% \section{}
% \label{}

\begin{thebibliography}{00}
\bibitem{zheng2008understanding}
Zheng, Y., Li, Q., Chen, Y., Xie, X., Ma, W.Y., 2008
\newblock Understanding mobility based on GPS data.
\newblock  Proceedings of the 10th international conference on Ubiquitous
  computing. ACM, pp. 312--321.

\bibitem{jiang2009characterizing}
Jiang, B., Yin, J., Zhao, S., 2009
\newblock Characterizing the human mobility pattern in a large street network.
\newblock {\em Physical Review E}, {\em 80},~021136.

\bibitem{belik2011natural}
Belik, V., Geisel, T., Brockmann, D.
\newblock Natural human mobility patterns and spatial spread of infectious
  diseases.
\newblock {\em Physical Review X} {\bf 2011}, {\em 1},~011001.

\bibitem{greenwood1985human}
Greenwood, M.J.
\newblock Human migration: Theory, models, and empirical studies.
\newblock {\em Journal of regional Science} {\bf 1985}, {\em 25},~521--544.

\bibitem{brockmann2006scaling}
Brockmann, D., Hufnagel, L., Geisel, T.
\newblock The scaling laws of human travel.
\newblock {\em Nature} {\bf 2006}, {\em 439},~462--465.

\bibitem{gonzalez2008understanding}
Gonzalez, M.C., Hidalgo, C.A., Barabasi, A.L.
\newblock Understanding individual human mobility patterns.
\newblock {\em Nature} {\bf 2008}, {\em 453},~779--782.

\bibitem{Jurdak2015}
Jurdak, R., Zhao, K., Liu, J., AbouJaoude, M., Cameron, M., Newth, D.
\newblock Understanding Human Mobility from Twitter.
\newblock {\em PLoS ONE} {\bf 2015}, {\em 10},~e0131469.

\bibitem{rhee2011levy}
Rhee, I., Shin, M., Hong, S., Lee, K., Kim, S.J., Chong, S.
\newblock On the levy-walk nature of human mobility.
\newblock {\em IEEE/ACM transactions on networking (TON)} {\bf 2011}, {\em
  19},~630--643.

\bibitem{sevtsuk2010does}
Sevtsuk, A., Ratti, C.
\newblock Does urban mobility have a daily routine? Learning from the aggregate
  data of mobile networks.
\newblock {\em Journal of Urban Technology} {\bf 2010}, {\em 17},~41--60.

\bibitem{kung2014exploring}
Kung, K.S., Greco, K., Sobolevsky, S., Ratti, C.
\newblock Exploring universal patterns in human home-work commuting from mobile
  phone data.
\newblock {\em PloS one} {\bf 2014}, {\em 9},~e96180.

\bibitem{thatcher2014living}
Thatcher, J.
\newblock Living on fumes: Digital footprints, data fumes, and the limitations
  of spatial big data.
\newblock {\em International Journal of Communication} {\bf 2014}, {\em
  8},~1765--1783.

\bibitem{hawelka2014geo}
Hawelka, B., Sitko, I., Beinat, E., Sobolevsky, S., Kazakopoulos, P., Ratti, C.
\newblock Geo-located Twitter as proxy for global mobility patterns.
\newblock {\em Cartography and Geographic Information Science} {\bf 2014}, {\em
  41},~260--271.

\bibitem{giannotti2008mobility}
Giannotti, F., Pedreschi, D.
\newblock {\em Mobility, data mining and privacy: Geographic knowledge
  discovery}, Springer Science \& Business Media,  2008.

\bibitem{crampton2014collect}
Crampton, J.W.
\newblock Collect it all: national security, Big Data and governance.
\newblock {\em GeoJournal} {\bf 2014}, pp. 1--13.

\bibitem{wu2014intra}
Wu, L., Zhi, Y., Sui, Z., Liu, Y.
\newblock Intra-urban human mobility and activity transition: Evidence from
  social media check-in data.
\newblock {\em PloS one} {\bf 2014}, {\em 9},~e97010.

\bibitem{hasan2013understanding}
Hasan, S., Zhan, X., Ukkusuri, S.V.
\newblock Understanding urban human activity and mobility patterns using
  large-scale location-based data from online social media.
\newblock  Proceedings of the 2nd ACM SIGKDD international workshop on urban
  computing. ACM,  2013, p.~6.

\bibitem{cho2011friendship}
Cho, E., Myers, S.A., Leskovec, J.
\newblock Friendship and mobility: user movement in location-based social
  networks.
\newblock  Proceedings of the 17th ACM SIGKDD international conference on
  Knowledge discovery and data mining. ACM,  2011, pp. 1082--1090.

\bibitem{noulas2012tale}
Noulas, A., Scellato, S., Lambiotte, R., Pontil, M., Mascolo, C.
\newblock A tale of many cities: universal patterns in human urban mobility.
\newblock {\em PloS one} {\bf 2012}, {\em 7},~e37027.

\bibitem{balcan2009multiscale}
Balcan, D., Colizza, V., Gon{\c{c}}alves, B., Hu, H., Ramasco, J.J.,
  Vespignani, A.
\newblock Multiscale mobility networks and the spatial spreading of infectious
  diseases.
\newblock {\em Proceedings of the National Academy of Sciences} {\bf 2009},
  {\em 106},~21484--21489.

\bibitem{tamerius2011global}
Tamerius, J., Nelson, M.I., Zhou, S.Z., Viboud, C., Miller, M.A., Alonso, W.J.
\newblock Global influenza seasonality: reconciling patterns across temperate
  and tropical regions.
\newblock {\em Environmental health perspectives} {\bf 2011}, {\em 119},~439.

\bibitem{tsou2015}
Tsou, M.H.
\newblock Research challenges and opportunities in mapping social media and Big
  Data.
\newblock {\em Cartography and Geographic Information Science} {\bf 2015}, {\em
  42},~70--74.

\bibitem{zheng2010geolife}
Zheng, Y., Xie, X., Ma, W.Y.
\newblock GeoLife: A Collaborative Social Networking Service among User,
  Location and Trajectory. {\bf 2010}.

\bibitem{becker2013human}
Becker, R., C{\'a}ceres, R., Hanson, K., Isaacman, S., Loh, J.M., Martonosi,
  M., Rowland, J., Urbanek, S., Varshavsky, A., Volinsky, C.
\newblock Human mobility characterization from cellular network data.
\newblock {\em Communications of the ACM} {\bf 2013}, {\em 56},~74--82.

\bibitem{sobolevsky2013delineating}
Sobolevsky, S., Szell, M., Campari, R., Couronn{\'e}, T., Smoreda, Z., Ratti,
  C.
\newblock Delineating geographical regions with networks of human interactions
  in an extensive set of countries.
\newblock {\em PLoS One} {\bf 2013}, {\em 8},~e81707.

\bibitem{twitterAPI}
Twitter.
\newblock Twitter streaming API.
\newblock {\em available from: https://dev.twitter.com/streaming/overview} {\bf
  2016}.

\bibitem{cranshaw2012livehoods}
Cranshaw, J., Schwartz, R., Hong, J.I., Sadeh, N.M.
\newblock The Livehoods Project: Utilizing Social Media to Understand the
  Dynamics of a City.
\newblock  ICWSM,  2012.

\bibitem{mitchell2013geography}
Mitchell, L., Frank, M.R., Harris, K.D., Dodds, P.S., Danforth, C.M.
\newblock The geography of happiness: Connecting twitter sentiment and
  expression, demographics, and objective characteristics of place {\bf 2013}.

\bibitem{longley2015geotemporal}
Longley, P.A., Adnan, M., Lansley, G., others.
\newblock The geotemporal demographics of Twitter usage.
\newblock {\em Environment and Planning A} {\bf 2015}, {\em 47},~465--484.

\bibitem{hagerstrand1985time}
H{\"a}gerstrand, T., others.
\newblock Time-geography: focus on the corporeality of man, society, and
  environment.
\newblock {\em The science and praxis of complexity} {\bf 1985}, pp. 193--216.

\bibitem{kwan2004geovisualization}
Kwan, M.P., Lee, J.
\newblock Geovisualization of human activity patterns using 3D GIS: a
  time-geographic approach.
\newblock {\em Spatially integrated social science} {\bf 2004}, {\em 27}.

\bibitem{andrienko2007designing}
Andrienko, N., Andrienko, G.
\newblock Designing visual analytics methods for massive collections of
  movement data.
\newblock {\em Cartographica: The International Journal for Geographic
  Information and Geovisualization} {\bf 2007}, {\em 42},~117--138.

\bibitem{maceachren2001research}
MacEachren, A.M., Kraak, M.J.
\newblock Research challenges in geovisualization.
\newblock {\em Cartography and Geographic Information Science} {\bf 2001}, {\em
  28},~3--12.

\bibitem{maceachren2004maps}
MacEachren, A.M.
\newblock {\em How maps work: representation, visualization, and design},
  Guilford Press,  2004.

\bibitem{andrienko2007visual}
Andrienko, G., Andrienko, N., Wrobel, S.
\newblock Visual analytics tools for analysis of movement data.
\newblock {\em ACM SIGKDD Explorations Newsletter} {\bf 2007}, {\em 9},~38--46.

\bibitem{black2012twitter}
Black, A., Mascaro, C., Gallagher, M., Goggins, S.P.
\newblock Twitter zombie: Architecture for capturing, socially transforming and
  analyzing the Twittersphere.
\newblock  Proceedings of the 17th ACM international conference on Supporting
  group work. ACM,  2012, pp. 229--238.

\bibitem{shvachko2010hadoop}
Shvachko, K., Kuang, H., Radia, S., Chansler, R.
\newblock The hadoop distributed file system.
\newblock  Mass Storage Systems and Technologies (MSST), 2010 IEEE 26th
  Symposium on. IEEE,  2010, pp. 1--10.

\bibitem{dean2008mapreduce}
Dean, J., Ghemawat, S.
\newblock MapReduce: simplified data processing on large clusters.
\newblock {\em Communications of the ACM} {\bf 2008}, {\em 51},~107--113.

\bibitem{gao2012exploring}
Gao, H., Tang, J., Liu, H.
\newblock Exploring Social-Historical Ties on Location-Based Social Networks.
\newblock  ICWSM,  2012.

\bibitem{buttenfield1991map}
Buttenfield, B.P., McMaster, R.B.
\newblock {\em Map Generalization: Making rules for knowledge representation},
  Longman Scientific \& Technical New York,  1991.

\bibitem{samet1984quadtree}
Samet, H.
\newblock The quadtree and related hierarchical data structures.
\newblock {\em ACM Computing Surveys (CSUR)} {\bf 1984}, {\em 16},~187--260.

\bibitem{clauset2009power}
Clauset, A., Shalizi, C.R., Newman, M.E.
\newblock Power-law distributions in empirical data.
\newblock {\em SIAM review} {\bf 2009}, {\em 51},~661--703.

\bibitem{reynolds2012truncated}
Reynolds, A.
\newblock Truncated L{\'e}vy walks are expected beyond the scale of data
  collection when correlated random walks embody observed movement patterns.
\newblock {\em Journal of The Royal Society Interface} {\bf 2012}, {\em
  9},~528--534.

\bibitem{zhao2015explaining}
Zhao, K., Musolesi, M., Hui, P., Rao, W., Tarkoma, S.
\newblock Explaining the power-law distribution of human mobility through
  transportation modality decomposition.
\newblock {\em Scientific reports} {\bf 2015}, {\em 5}.

\end{thebibliography}

\end{document}
